\documentclass[margin,line]{resume}
\usepackage[hidelinks]{hyperref}
\usepackage{tabto}

\begin{document}
\name{\Large Nathan Dunn}
\begin{resume}
    \section{\mysidestyle Contact\\Information}

    Phone: (413) 265-1607 \tabto{5cm} LinkedIn: \url{https://www.linkedin.com/in/nathan-dunn}\\
    Email: ndunn@umass.edu \tabto{5cm}  Github: \url{https://github.com/njdu}\\
    %\begin{tabular}{l l}
    %Phone: (413) 265-1607 & LinkedIn: %\url{https://www.linkedin.com/in/nathan-dunn}\\
    %Email: ndunn@umass.edu & Github: %\url{https://github.com/njdu}\\
    %\end{tabular}
    \vspace{0mm}\\\vspace{-1cm}

    \section{\mysidestyle Education}

    \textbf{University Of Massachusetts Amherst} \hfill \textbf{Graduating May 2017}\\
    \textsl{B.S., Computer Systems Engineering} \hfill
    GPA: 3.94


    \section{\mysidestyle Professional\\Experience}

    \textbf{Brightergy LLC}, Kansas City, MO \vspace{2mm}\\\vspace{1mm}%
    \textsl{Software Development Intern} \hfill \textbf{Oct 2016 -- Jan 2017}\\
    Working remotely, I helped to sustain the DevOps culture by assisting with QA testing and developing new ways to monitor key production statistics.  Some of my responsibilities included:
    \begin{itemize}
        \item Developing unit tests for back-end APIs
        \item Contributing to an open-source Elixir project to display automated script/testing results on company dashboards
    \end{itemize}

    \textbf{Fidelity Investments}, Merrimack, NH \vspace{2mm}\\\vspace{1mm}%
    \textsl{Software Development Intern} \hfill \textbf{May 2016 -- Aug 2016}\\
   I served as the front-end developer on the complete rewrite of an internal web application used to display relevant company financial data to managers/executives. Utilizing Angular 1.5 and Typescript, I created a modular, component based architecture. I communicated regularly with offsite backend developer and graphic designer, to coordinate and deliver on product features. The application is scheduled to go live in the first quarter of 2017.

    \textbf{University of Connecticut}, Storrs, CT \vspace{2mm}\\\vspace{1mm}%
    \textsl{Undergraduate Researcher} \hfill \textbf{May 2015 -- Apr 2016}\\
    Through a Research Experience for Undergraduates program funded by the National Science Foundation, I worked in a group investigating methods to identify counterfeit integrated circuits. Some of my projects included:
    \begin{itemize}
     \item Developing a PHP MVC web application for industry and academic professionals to share counterfeit inspection results
     \item Writing a MATLAB image processing program  to identify scratches on integrated circuit casings
     \item Assisting in the writing and editing of an academic conference paper
    \end{itemize}

    \textbf{Depuy Synthes Orthopaedics}, Raynham, MA \vspace{2mm}\\\vspace{1mm}%
    \textsl{Foundry Engineering Co-Op} \hfill \textbf{Jan 2013 -- June 2013}\\
    Worked with Foundry Engineers to improve manufacturing processes within an investment casting foundry. Major initiatives included:
    \begin{itemize}
        \item  Validation of new viscosity measuring equipment to meet process specifications
        \item Production of training video for new operators to ensure consistent assembly of wax sprues
        \item Creating a new Microsoft Access organizational system for metallurgical samples.
    \end{itemize}


\section{\mysidestyle Projects}

    \textbf{Earbeamer}\vspace{2mm}\\\vspace{1mm}%
    \textsl{Senior Design Project} \hfill \textbf{September 2016 - Present}\\
    Currently building a beamforming hearing aid system that uses image and audio processing to dynamically track and isolate the audio streams of all individuals within a room. A user can then amplify or attenuate each audio stream at will. I implemeneted target tracking in C++ using an Xbox Kinect, and designed the microphone array geometry to maximize directivity

   \section{\mysidestyle Selected Publications}
   N. Asadizanjani, S. Gattigowda, N. Dunn, D. Forte, and M. Tehranipoor, "A Database for Counterfeit Electronics and Automatic Defect Detection Based on Image processing and Machine Learning," \textsl{Int. Symposium on Testing and Failure Analysis (ISTFA)}, 2016.
\vspace{-2mm}

    \section{\mysidestyle Programming\\Experience}

    \emph{Languages:} C++, Java, Typescript/Javascript, Elixir, MATLAB, Verilog, MIPS Assembly, Bash\\
    \emph{Web Technologies:} AngularJS, Phoenix Framework, HTML, CSS, Bootstrap, Jasmine Testing\\
    \emph{Other Skills:} Bash Scripting, MySQL, PostgreSQL, Linux/Unix,
\end{resume}
\end{document}
